A word-sense representation for documents based on information value and word sense disambiguation

### 2014-04-03 paper/refactor.tex
Move acknowledgments upwards.
Fix layout.
Definitively fix layout...I hope.

%% ADDITIONAL OPTIONAL STYLE FILES
%\usepackage[dvips]{graphicx}
%\usepackage{pnastwof}
\usepackage{amssymb,amsfonts,amsmath}
\usepackage[utf8]{inputenc}
\usepackage[dvips]{graphicx}
\usepackage{bookmark}
\usepackage{color}
\usepackage{array}
\usepackage{setspace}
\usepackage{longtable}
\usepackage[hmargin=2cm,vmargin=2.5cm]{geometry}
\usepackage{booktabs}
\usepackage{colortbl}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcommand{\myrowcolour}{\rowcolor[gray]{0.925}}
  \newcommand{\cheading}[2]{\textbf{#1\hfill #2}}

@@

But this weighted set of top words has the problem of polysemy, typical in the field of nlp. Polysemy occurs when a term has more than one sense or meaning, for example: the term 'bank' can refer to a financial institution or to a land formation, thus, it is polysemic. In order to resolve this limitation, we implement a basic algorithm of word-sense disambiguation based on wordnet's synsets and we apply it over the top words, using as disambiguation context the whole document. We obtain, then, the \textit{top senses} of a document, this is, a ranked set of wordnet synsets that work like a representation of the given document.

@@

\subsubsection{Word-senses evaluation set}

@@

\input{handpicked_table}
\newpage

@@

%\subsubsection{Similarities with chosen concepts}
\newpage
\input{results_sim_tables}

@@

\input{apendices}
% *SynsetAnalyzer
%   *Synset
%   *path, lch, wup
% *judge_word
% *judge_doc
% *judge_year
% Dado un conjunto de palabras, definimos la distancia de una palabra a este conjunto como 
%

@@

>>>>

%% ADDITIONAL OPTIONAL STYLE FILES
%\usepackage[dvips]{graphicx}
%\usepackage{pnastwof}
\usepackage{amssymb,amsfonts,amsmath}
\usepackage[utf8]{inputenc}
\usepackage[dvips]{graphicx}
\usepackage{bookmark}
\usepackage{color}
\usepackage{array}
\usepackage{setspace}
\usepackage{longtable}
\usepackage[hmargin=2cm,vmargin=2.5cm]{geometry}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{dblfloatfix}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcommand{\myrowcolour}{\rowcolor[gray]{0.925}}
  \newcommand{\cheading}[2]{\textbf{#1\hfill #2}}

@@

But this weighted set of top words has the problem of polysemy, typical in the field of nlp. Polysemy occurs when a term has more than one sense or meaning, for example: the term `bank' can refer to a financial institution or to a land formation, thus, it is polysemic. In order to resolve this limitation, we implement a basic algorithm of word-sense disambiguation based on wordnet's synsets and we apply it over the top words, using as disambiguation context the whole document. We obtain, then, the \textit{top senses} of a document, this is, a ranked set of wordnet synsets that work like a representation of the given document.

@@

\subsubsection{Word-senses evaluation set}
\input{handpicked_table}

@@

@@

%\subsubsection{Similarities with chosen concepts}
\input{results_sim_tables}

@@

@@

\input{apendices}
